%% ----------------------------------------------------------------
%% Introduction.tex
%% ---------------------------------------------------------------- 
\chapter{Introduction} \label{Chapter:Introduction}

\section{Project Problem}

In modern, fast-paced lives, urban mobility is an integral aspect that significantly impacts our daily routines. 
One of the most pervasive challenges in urban areas is the issue of traffic congestion, causing delays, frustration, and inefficiencies in transportation systems. 
This poses high requirements for traffic management and navigation systems addressing these problems. 
In the topic of traffic management and planning, accurate prediction of vehicles and proactively suggesting optimal routes in urban road networks is one of the important tasks to improve traffic efficiency, and safety, and to mitigate traffic congestion. 
This project seeks to explore the realm of traffic prediction, employing deep learning techniques to provide accurate insights into future traffic conditions. 

This project involves the development of a sophisticated model using recurrent neural network (RNN)-based methods. 
The model will not only consider historical traffic data but also incorporate environmental factors such as time of day, 
whether it is a weekday, and whether it is a holiday. By embracing a comprehensive approach, we aim to create a predictive system that can adapt to various conditions.

\section{Goals}

The main milestones to be done for this project iterates:

\begin{itemize}
    \item Gather appropriate datasets consisting of road information, and congestion situations in a time sequence. 
    \item Modify the datasets to find some features that are vital for prediction. 
    \item Create a deep learning model to predict the average travel time of vehicles at a certain time in each road section.
    \item Evaluate the performance and accuracy of the model.
    \item Find ways to improve the performance, and evaluate again.
    \item Create a pathfinding algorithm, and use the result of the prediction to make decisions on optimal routes. 
\end{itemize}